Efficient pedigree recording for fast population genetics simulation

### 2018-01-22 forwards_paper.tex

\paragraph{Essential steps in tree sequence recording}
To record a tree sequence, including mutations,
a simulator must record:
\begin{itemize}
    \item the birth time of each individual in the Node Table,
    \item the genetic segments each individual inherits from her parents in the Edge Table, and
    \item the individual each new mutation occurs in, and the derived state in the Mutation Table,
        adding also to the Site Table if the site is previously unmutated.
\end{itemize}
Recall that here we mean ``\emph{haploid} individual'', i.e., gamete.
Before simplification, time must be translated to ``time ago'' if it is not already,
and the tables must be sorted.
Algorithm~\algref{W} avoided both of these details since $t$ denotes
``time until the end of the simulation'',
and nonoverlapping generations ensure that the tables will be already sorted.
Finally, since $\tsimplify{P', \Nt, \Et}$ results in the $N$ individuals in $P'$
being relabeled in \msprime{}'s tables as $0, 1, \ldots, N-1$,
there must be bookkeeping that keeps in sync the individual IDs as recorded by the simulator
with the node IDs recorded in the tables.

>>>>

\paragraph{Essential steps in tree sequence recording}
To record a tree sequence, including mutations,
a simulator must record:
\begin{itemize}
    \item the birth time of each individual in the Node Table,
    \item the genetic segments each individual inherits from her parents in the Edge Table, and
    \item the individual each new mutation occurs in, and the derived state in the Mutation Table,
        adding also to the Site Table if the site is previously unmutated.
\end{itemize}
Recall that here we mean ``\emph{haploid} individual'', i.e., gamete.
Before simplification, time must be translated to ``time ago'' if it is not already.
which was avoided in Algorithm~\algref{W} since there $t$ denoted
``time until the end of the simulation''.
Furthermore, since $\tsimplify{P', \Nt, \Et}$ results in the $N$ individuals in $P'$
being relabeled in \msprime{}'s tables as $0, 1, \ldots, N-1$,
there must be bookkeeping that keeps in sync the individual IDs as recorded by the simulator
with the node IDs recorded in the tables.
% Finally, the first step in simplification is to \emph{sort} the tables
% according to several criteria, for algorithmic efficiency,
% as described in the documentation.
